`SCPCL001114` - Exploration of gene set based methods for tumor cell assignment

### 2024-07-17 analyses/cell-type-ewings/exploratory_analysis/annotation_notebooks/SCPCS000752/SCPCL001114_tumor-gene-expression-exploration.Rmd
move consensus to be last

classification_df |> 
  tidyr::pivot_longer(
    cols = ends_with("classification"),
    names_to = "method",
    values_to = "classification"
  ) |> 
  dplyr::mutate(
    method = forcats::fct_recode(method, !!!method_levels)) |> 
  ggplot(aes(x = UMAP1, y = UMAP2, color = classification)) +
  geom_point(size = 0.1, alpha = 0.5) +
  facet_wrap(vars(method)) +
  guides(color = guide_legend(override.aes = list(size = 3, alpha = 1)))
```

@@

# create a density plot showing the distribution of marker gene expression across classification methods 
marker_density_df <- plot_markers_df |>
  # add new methods 
  dplyr::left_join(new_classification_df, by = c("barcodes")) |> 
  tidyr::pivot_longer(
    cols = ends_with("classification"),
    names_to = "method",
    values_to = "classification"
  ) |> 
  dplyr::mutate(
    method = forcats::fct_recode(method, !!!method_levels)
  )

@@

```{r fig.height=7}
geneset_plot_df |> 
  # add new methods 
  dplyr::left_join(new_classification_df, by = c("barcodes", "ref_marker_gene_classification")) |> 
  tidyr::pivot_longer(
    cols = ends_with("classification"),
    names_to = "method",
    values_to = "classification"
  ) |> 
  dplyr::mutate(
    method = forcats::fct_recode(method, !!!method_levels)) |> 
  ggplot(aes(x = mean_score, color = classification)) +
  geom_density(bw = 0.05) +
  facet_grid(rows = vars(method), 
             cols = vars(geneset))
```

>>>>

classification_df |> 
  tidyr::pivot_longer(
    cols = ends_with("classification"),
    names_to = "method",
    values_to = "classification"
  ) |> 
  dplyr::mutate(
    method = forcats::fct_recode(method, !!!method_levels),
    method = forcats::fct_relevel(method, "Consensus", after = Inf)) |> 
  ggplot(aes(x = UMAP1, y = UMAP2, color = classification)) +
  geom_point(size = 0.1, alpha = 0.5) +
  facet_wrap(vars(method)) +
  guides(color = guide_legend(override.aes = list(size = 3, alpha = 1)))
```

@@

# create a density plot showing the distribution of marker gene expression across classification methods 
marker_density_df <- plot_markers_df |>
  # add new methods 
  dplyr::left_join(new_classification_df, by = c("barcodes")) |> 
  tidyr::pivot_longer(
    cols = ends_with("classification"),
    names_to = "method",
    values_to = "classification"
  ) |> 
  dplyr::mutate(
    method = forcats::fct_recode(method, !!!method_levels),
    method = forcats::fct_relevel(method, "Consensus", after = Inf)
  )

@@

```{r fig.height=7}
geneset_plot_df |> 
  # add new methods 
  dplyr::left_join(new_classification_df, by = c("barcodes", "ref_marker_gene_classification")) |> 
  tidyr::pivot_longer(
    cols = ends_with("classification"),
    names_to = "method",
    values_to = "classification"
  ) |> 
  dplyr::mutate(
    method = forcats::fct_recode(method, !!!method_levels), 
    method = forcats::fct_relevel(method, "Consensus", after = Inf)) |> 
  ggplot(aes(x = mean_score, color = classification)) +
  geom_density(bw = 0.05) +
  facet_grid(rows = vars(method), 
             cols = vars(geneset))
```
